This is an example of article title

### 2019-09-24 paper.tex
attemp to fix

Naturally, tables support \texttt{map}, \texttt{reduce}, \texttt{groupreduce}, \texttt{groupby} and \texttt{join} operations. We will defer their discussion to the API documentation of JuliaDB \cite{juliadbapi}. Read the Sectoin \ref{sec:sort} for more about the implementation of some of these operations.

@@

A \texttt{StringArray}'s stores a collection of strings with less memory indirection than a usual array of strings. Its memory layout is show in in Figure \ref{fig:stringarray}. The contents of strings (unicode character codes) are packed into a contiguous buffer of 8-bit unsigend integers. \texttt{StringArray} also stores the lengths of each string and the index (offset) at which each of them starts. Although it would suffice to store just the length of each string, storing offset also allows us to implement efficient mutation operations. Setting an element of the array appends the new string to the end of the buffer and replaces the length and offset with the corresponding new length and offsets for that item. Operations such as \texttt{sort!} and \texttt{permute!} (in place permutation of items) can simply modify the length and offset arrays and leave the buffer unmodified. Wherever suitable, in code internal to JuliaDB, we create \texttt{WeakRefString} instead of creating String objects when we index into a \texttt{StringArray}, this greatly reduces GC-load when dealing with string columns in operations such as groupby and join. Some advantages of a StringArray are 1) the buffer, and the length and offset vectors can be memory mapped to disk. 2) it takes less serialization overhead to send the same over the wire to another process.

@@

$$\begin{equation}
  \begin{split}
    \sigma_G^2 &= \left( \left.\frac{\partial G}{\partial a}\right\vert_{a =
        \bar{a}} \sigma_a \right)^2 + \left( \left.\frac{\partial G}{\partial
          b}\right\vert_{b = \bar{b}} \sigma_b \right)^2 + \left(
      \left.\frac{\partial G}{\partial c}\right\vert_{c = \bar{c}} \sigma_c
    \right)^2 + \cdots \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}} \sigma_{ab} + 2
    \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}}
    \sigma_{ac} \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}} \sigma_{bc} +
    \cdots
  \end{split}
\end{equation}
$$

@@

\begin{figure*}[h]
    \centering \includegraphics[width=5in]{image4.png} \caption{Query times for 3 different query types across various systems}
    \label{fig:nyctaxiquery} 
    \caption{Query performance comparison with other systems. Query 1: average fare amount by type of vendor. Query 2: number of trips grouped by number of passengers and day of week. Query 3: number of trips grouped by number of passengers and even and odd days of week. (Monday, Wednesday, Firday are even, rest are odd).
\end{figure*}

>>>>

Naturally, tables support \texttt{map}, \texttt{reduce}, \texttt{groupreduce}, \texttt{groupby} and \texttt{join} operations. We will defer their discussion to the API documentation of JuliaDB \cite{juliadbapi}. Read the Section~\ref{sec:sort} for more about the implementation of some of these operations.

@@

A \texttt{StringArray}'s stores a collection of strings with less memory indirection than a usual array of strings. Its memory layout is show in in Figure~\ref{fig:stringarray}. The contents of strings (unicode character codes) are packed into a contiguous buffer of 8-bit unsigend integers. \texttt{StringArray} also stores the lengths of each string and the index (offset) at which each of them starts. Although it would suffice to store just the length of each string, storing offset also allows us to implement efficient mutation operations. Setting an element of the array appends the new string to the end of the buffer and replaces the length and offset with the corresponding new length and offsets for that item. Operations such as \texttt{sort!} and \texttt{permute!} (in place permutation of items) can simply modify the length and offset arrays and leave the buffer unmodified. Wherever suitable, in code internal to JuliaDB, we create \texttt{WeakRefString} instead of creating String objects when we index into a \texttt{StringArray}, this greatly reduces GC-load when dealing with string columns in operations such as groupby and join. Some advantages of a StringArray are 1) the buffer, and the length and offset vectors can be memory mapped to disk. 2) it takes less serialization overhead to send the same over the wire to another process.

@@

$$\begin{equation}
  \begin{align}
    \sigma_G^2 &= \left( \left.\frac{\partial G}{\partial a}\right\vert_{a =
        \bar{a}} \sigma_a \right)^2 + \left( \left.\frac{\partial G}{\partial
          b}\right\vert_{b = \bar{b}} \sigma_b \right)^2 + \left(
      \left.\frac{\partial G}{\partial c}\right\vert_{c = \bar{c}} \sigma_c
    \right)^2 + \cdots \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}} \sigma_{ab} + 2
    \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}}
    \sigma_{ac} \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}} \sigma_{bc} +
    \cdots
  \end{align}
\end{equation}$$

@@

\begin{figure*}[h]
    \centering \includegraphics[width=5in]{image4.png}
    \label{fig:nyctaxiquery} 
    \caption{Query performance comparison with other systems. Query 1: average fare amount by type of vendor. Query 2: number of trips grouped by number of passengers and day of week. Query 3: number of trips grouped by number of passengers and even and odd days of week. (Monday, Wednesday, Firday are even, rest are odd).}
\end{figure*}
